Picky with peakpicking: assessing chromatographic peak quality with simple

### 2023-06-12 manuscript/manuscript.Rmd
Full rerun of entire analysis, more metric discussion

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval=FALSE)
knitr::opts_knit$set(root.dir = '..')
options(readr.show_col_types = FALSE)
options(tidyverse.quiet = TRUE)
library(tidyverse)
library(RaMS)
```

@@

```{r full model estimate csv write}
set.seed(123)

@@

```{r Supp figure param distributions, warning=FALSE}
both_datasets <- list(MESOSCOPE=MS3000_features, Falkor=FT2040_features) %>%
  bind_rows(.id = "dataset") %>%
  filter(feat_class%in%c("Good", "Bad")) %>%
  mutate(feat_bin=ifelse(feat_class=="Good", 1, 0))
pdf(file = "manuscript/supplement/metric_distributions.pdf", width = 6.5, height = 4)
both_datasets %>%
  select(mean_mz:area_cor) %>%
  colnames() %>%
  walk(function(chosen_param){
    hist_gp <- both_datasets %>%
      ggplot() +
      geom_hline(yintercept = 0) +
      geom_histogram(aes(x=get(chosen_param), fill=feat_class), bins=40) +
      scale_fill_manual(breaks = c("Bad", "Good"), values = c("#a41118", "#f4bb23")) +
      labs(y="# of mass features", x=chosen_param) +
      theme_bw() +
      theme(legend.direction = "horizontal", legend.position = "none") +
      facet_wrap(~dataset, ncol=1, scales = "free_y")
    log_gp <- both_datasets %>%
      ggplot(aes(x=get(chosen_param), y=feat_bin)) +
      geom_jitter(aes(color=feat_class), alpha=0.2, height = 0.1, width=0) +
      geom_smooth(method = "glm", method.args=list(family=binomial), formula="y~x", color="black") +
      scale_color_manual(breaks = c("Bad", "Good"), values = c("#a41118", "#f4bb23")) +
      scale_y_continuous(breaks = c(0, 1), labels = c("Bad", "Good"), name=NULL) +
      labs(x=chosen_param) +
      theme_bw() +
      theme(legend.position = "none", 
            axis.text.y = ggtext::element_markdown(
              color = c("#a41118", "#f4bb23"), face = "bold")) +
      facet_wrap(~dataset, ncol=1, scales = "free_y")
    egg::ggarrange(hist_gp, log_gp, nrow=1)
  }, .progress = TRUE)
graphics.off()
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval=TRUE)
knitr::opts_knit$set(root.dir = '..')
options(readr.show_col_types = FALSE)
options(tidyverse.quiet = TRUE)
library(tidyverse)
library(RaMS)
```

@@

```{r full model estimate csv write}
set.seed(123)
both_datasets <- list(MESOSCOPE=MS3000_features, Falkor=FT2040_features) %>%
  bind_rows(.id = "dataset") %>%
  filter(feat_class%in%c("Good", "Bad")) %>%
  mutate(feat_bin=ifelse(feat_class=="Good", 1, 0))

@@

```{r Supp figure param distributions, warning=FALSE}
both_datasets <- list(MESOSCOPE=MS3000_features, Falkor=FT2040_features) %>%
  bind_rows(.id = "dataset") %>%
  filter(feat_class%in%c("Good", "Bad")) %>%
  mutate(feat_bin=ifelse(feat_class=="Good", 1, 0))
pdf(file = "manuscript/supplement/metric_distributions.pdf", width = 6.5, height = 4)
both_datasets %>%
  select(mean_mz:iso_area_cor) %>%
  colnames() %>%
  walk(function(chosen_param){
    hist_gp <- both_datasets %>%
      ggplot() +
      geom_hline(yintercept = 0) +
      geom_histogram(aes(x=get(chosen_param), fill=feat_class), bins=40) +
      scale_fill_manual(breaks = c("Bad", "Good"), values = c("#a41118", "#f4bb23")) +
      labs(y="# of mass features", x=chosen_param) +
      theme_bw() +
      theme(legend.direction = "horizontal", legend.position = "none") +
      facet_wrap(~dataset, ncol=1, scales = "free_y")
    log_gp <- both_datasets %>%
      ggplot(aes(x=get(chosen_param), y=feat_bin)) +
      geom_jitter(aes(color=feat_class), alpha=0.2, height = 0.1, width=0) +
      geom_smooth(method = "glm", method.args=list(family=binomial), formula="y~x", color="black") +
      scale_color_manual(breaks = c("Bad", "Good"), values = c("#a41118", "#f4bb23")) +
      scale_y_continuous(breaks = c(0, 1), labels = c("Bad", "Good"), name=NULL) +
      labs(x=chosen_param) +
      theme_bw() +
      theme(legend.position = "none", 
            axis.text.y = ggtext::element_markdown(
              color = c("#a41118", "#f4bb23"), face = "bold")) +
      facet_wrap(~dataset, ncol=1, scales = "free_y")
    egg::ggarrange(hist_gp, log_gp, nrow=1)
  }, .progress = TRUE)
graphics.off()
```
